---
title: "A3: SPL Library Checkouts"
output: html_document
---

### Introduction

The Seattle Public Library has been collecting data about items checked out by people ever since 2005! This includes, the book, type of checkout, whether the item is physical or virtual, and much more! I chose to anaylze physical / virtual books in my first chart for the past 4 years, the types of checkout people were using over the past 6 years, and then finding out the amount of checkouts for some of my favorite authors!

### Summary Information

I found 5 values that I was interested in throughout my charts! My first value was that in 2020-01-01, there was 274834 people who had physical book checkouts while there was only 79641 visual book (or ebook) in 2021-01-01, visual book (ebook) had hit their highest count of people who checkout ebooks with 103130, which isn't even close to a regular phsyical book checkout! A physical book highest checkout was 289311 and that is in 2023-01-01. Another value that I found interesting was in my last chart, where in 2020 Suzanne Collins had 800 checkouts on books! And compared to another author (Veronica Roth) she had a really big difference.

### The Dataset

The Seattle Public Schools had published this data. There were smaller data sets that were given, as I had used the dataset about items checked out at least 10 times a month from 2017-2023. There were multiple different columns or parameters that these datasets had, for things such as usage, checkout type, material type, dates, title of the book, etc. I think some limitations on this data might be from the books that get lost or when someone doesn't check out a book / check back in. I think that there is another problem with the data as sometimes the creator (or author) would have sometimes their last name first and so filtering through the data can sometimes lead to not include the whole data about an author. Ethically might be questioned if Seattle Public School released the names of the people who check out the books, As sometimes people might not want to be shown what they are reading! Other than that, I don't really know any other possible limitations.

### First Trends Over Time Chart

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("chart_1.R")}
```

For my first chart, I chose to showcase the difference of physical book vs ebook throughout the last 4 years. I chose this because I questioned if there was going to be a dramatic change because of the pandemic. However, with looking at the chart, it is easy to tell that even through the pandemic, people still had more physical books than they had ebooks.

``````{r, echo = FALSE, warning = FALSE, message = FALSE, code = readLines("chart 2.R")}
```


### Second Trends Over Time Chart

For my second chart, I decided to shwocase the difference of checkout types over 6 years! The types of checkouts that the data had weren't that big, but it seemed like each checkout type coordinated with something. Like how Freegal rental was for music.

I assumed that Horizon would lead the chart (as this was the checkout for most novels) and it came out true! It made sense, because I don't think too many people go to libraries to rent out music / movies anymore. Because we either use apple music/spotify or stream movies!


### Your Choice

For my last chart, I decided to show a few of my favorite authors! I chose Suzanne Collins, Rick Riodarn, and Veronica Roth. I couldn't for some reason, be able to get Rick Riodarn into the graph, but he was the author that created the percy jackson series! The chart showed the amount of checkouts from the Seattle Public Library through 2019 - 2023.

I would assume Suzzane Collins would be on the top, as she was the creator of Hunger Games, and that book is a classic. Veronica Roth created Divergent (and even though I liked it, a lot more people know about hunger games) 

\`\`\``{r, echo = FALSE, code = readLines("chart2_example.R")}`
